\section{Analysis}
\label{sec:analysis}
\lhead{\thesection \space Analysis}

TODO Marco

\subsection{Epics}
\label{ssec:epics}

TODO Marco

\subsubsection{Use Case Diagram}
\label{sssec:use_case_diagram}

TODO Marco

\subsubsection{Epic 1 - TODO Add Name}
\label{sssec:epic1}

TODO Marco

\subsubsection{Epic 2 - Promotion Code}
\label{sssec:epic2}
In addition to Epic 1, a coach user should be able to use a trial promotion code if he / she doesn't have the regular "\textit{VOTE4FUN}" feature to manage and start a \textit{Vote4Fun} poll for his / her team. 
\newline
This trial includes (a combination of):
\begin{itemize}
    \item A trial period in days
    \item A  maximum number of  voting polls to be created and managed
\end{itemize}
The period and number of polls for each trial code should be flexible. 
\newline
The trial code can be received via email with a \textit{promotion link, promotion code (string of characters)} or as a \textit{notification} on his /  her phone. 
\newline
\newline
The following requirements were given for this epic:
\begin{itemize}
    \item UR – 2.1 
    \newline
    A coach can open a view (position to be determined) to enter a trial code for managing Vote4Fun polls if and only if the user does not have the Vote4Fun permission.
    \item UR – 2.2
    \newline
    A coach can enter and submit a trial code.
    \item UR – 2.3 
    \newline
    A user receives a confirmation after entering the trial code.
    \item UR – 2.4 
    \newline
    A user receives a positive confirmation after entering a valid trial code.
    \item UR – 2.5 
    \newline
    A user receives a negative confirmation after entering an invalid trial code.
    \item UR – 2.6
    \newline
    A user can create and manage Vote4Fun polls after entering a valid trial code.
    \item UR – 2.7 
    \newline
    A user can see the remaining trial period / number of polls to be managed.
    \item UR – 2.8
    \newline
    A user with the app installed can click on an email promotion link to have the promotion code entered automatically.
    \item UR – 2.9 
    \newline
    A user with the app installed can click on a notification to have the promotion code entered automatically.
\end{itemize}

\subsubsection{Epic 3 - TODO Add Name}
\label{sssec:epic3}

TODO Patrick

\subsection{Application Architecture}
\label{ssec:application_architecture}

TODO Marco

\subsection{Software Requirements Specification}
\label{ssec:software_requirements_specification}

TODO Marco