\section*{Summary}
\addcontentsline{toc}{section}{Summary}

Students of the 7th semester of the Software Engineering/Business Informatics course of Fontys University of Applied Sciences Venlo worked in the module SoFa for a real customer. All previously learned skills throughout the studies needed to be applied in this module. Having interviews with the customer, analysing problems, designing solutions and implementing code are important skills in this project. Students were guided by a teacher to achieve the best outcome of the project. 
\newline
The customer \textit{Connected.Football} wants to have an extension for their current application that runs on mobile phones. The current application is meant to help football players and coaches to improve their training strategy. With the help of the developed extension users in the role of coaches are able to set up polls with a deadline for their respective teams and let members in their team vote for exercises that the coach pre-selected. The complete extension also enables a coach to invite players who have not installed the application on their phones to participate as a guest.
\newline
To develop this extension, \textit{JavaScript} is used as a language with \textit{ECMAScript 6} and frameworks like \textit{React Native}, \textit{recompose} and \textit{GraphQL} that improve the abilities of \textit{JavaScript}. With the help of \textit{React Native} mobile applications can be build in \textit{JavaScript} and can be compiled into native \textit{Android} and \textit{iOS} code. This framework allows fast prototype development without having in-depth knowledge of native mobile application development.